\phantomsection     % this command ensures the internal links will be correct
\cftaddtitleline{toc}{section}{Acknowledgements}{}
\section*{Acknowledgements}

I would like to express my deeply thanks to my thesis supervisor, Associate Professor Antti Knutas, for his support and counsel throughout this project. His expertise in civic technology software engineering was instrumental in shaping my research and keeping me focused. I especially appreciate his insightful feedback.

I am particularly grateful to my classmates, espicially Nan Yang and Roshan Devullapalli, for their invaluable co-operation and encouragement throughout this master program. Their willingness to brainstorm ideas and provide encouragement proved to be a tremendous help, especially during the thesis development stage. My experience as a teammate in previous courses fostered a strong foundation for collaboration, making this journey all the more rewarding.

My heartfelt thanks to my friends in Lahti and Helsinki for their incredible support during my time in Finland.

Last I would also like to express the love to my family, my relatives and especially my mother for her unwavering support. Her constant encouragement, especially during challenging moments, motivated me to persevere and finish my thesis. I am truly fortunate to have her in my life.

Despite my commitment, I'm aware that this project is still inadequate and contains inevitable errors. I would like to receive feedback from lecturers in order to improve furthermore.

\textit{Duc Thinh Tran} \\
\textit{Lahti, May 2024}



\clearpage % This command will start the next section from the new page

