%% Info page
\section*{Instructions for using the LUT thesis template}

{\color{red}This document is a template that you can use to write your final thesis at LUT University. It meets the requirements for the content, structure, and layout of the BSc and MSc theses as well as the accessibility criteria for material published in the LUTPub repository. It is especially important that you use the template in formulating the title page, abstracts, table of contents, list of references, and citations.

The template is applied in all BSc and MSc thesis projects that start after 11 August 2021.

The actual thesis template starts on the following page. Write your own thesis using this template and delete the introductory texts (e.g. this info page) and other content in the template that you do not need.

The appendices include important instructions – remember to read them as well. The thesis supervisor can give additional instructions.

In addition, read other thesis guidelines released by the Lappeenranta–Lahti University of Technology LUT: 
\begin{itemize}
    \item Thesis instructions in the \href{https://elut.lut.fi/en/completing-studies/theses}{\textcolor{blue}{eLUT portal}}
    \item LUT Academic library, \href{https://www.lut.fi/en/about-us/lut-academic-library/theses-and-dissertations}{\textcolor{blue}{pages for thesis students and researchers}} 
    \item LUT Academic library \href{https://libguides.lut.fi/informationliteracy}{\textcolor{blue}{information retrieval guide}}
    \item LUT Academic library, \href{https://libguides.lut.fi/copyright/}{\textcolor{blue}{copyright guidelines}} 
    \item LUT University, \href{https://elut.lut.fi/en/completing-studies/rules-and-regulations/ethical-guidelines-and-guidelines-handling-misconduct}{\textcolor{blue}{Ethical guidelines}} 
    \item Plagiarism detector \href{https://elut.lut.fi/en/it-instructions-study-tools/turnitin}{\textcolor{blue}{Turnitin}} guidelines for LUT students
    \item LUT University, \href{https://elut.lut.fi/en/completing-studies/rules-and-regulations/ai-based-tools-policies}{\textcolor{blue}{AI-based tools policies}}
    \item Graduation process and instructions in the \href{https://elut.lut.fi/en/graduation}{\textcolor{blue}{eLUT portal}}
\end{itemize}
}

\clearpage  % This command will start the next section from the new page

