%% This section adds chapter 1
\section{Introduction}
% example entries for nomenclature. These entries should be given throughout the text right after the symbol is used the first time. If "refpage" option is given, the corresponding page number is shown in nomenclature. The following nomenclature groups are used; A=Latin, B=Greek, C=Subscripts, D=Superscripts, E=Abbreviations, F=Dimensionless. This letter code should be placed first inside the [] brackets. The following letters inside square brackets [] are used to alphabetically sort the symbols and abbreviations in the list. The symbol or abbreviation itself is defined within the curly braces {} after the square brackets. The $$ signs create an equation form, i.e. a variable in italics. Inside the latter brackets, the legend and the unit are defined with the \nounit{} definition. For units, italics can be removed with the \mathrm{} command. See instructions https://www.overleaf.com/learn/latex/Nomenclatures or https://www.ctan.org/pkg/nomencl. 
% A=Latin letters
\nomenclature[Aa1]{$A$}{area\nomunit{$\mathrm{m^2}$}}
\nomenclature[Aa2]{$a$}{constant}
\nomenclature[Acd]{$C_D$}{drag coefficient}
\nomenclature[Acp]{$c_p$}{specific heat capacity at constant pressure\nomunit{$\mathrm{J/(kgK)}$}}
\nomenclature[Acv]{$c_v$}{specific heat capacity at constant volume\nomunit{$\mathrm{J/(kgK)}$}}
\nomenclature[Ad]{$d$}{diameter\nomunit{$\mathrm{m}$}}
\nomenclature[AF]{$\mathbf{F}$}{force vector\nomunit{$\mathrm{N}$}}
\nomenclature[Af]{$f$}{frequency\nomunit{$\mathrm{1/s,Hz}$}}
\nomenclature[Ag]{$g$}{acceleration due to gravity\nomunit{$\mathrm{m/s^2}$}}
\nomenclature[Ah]{$h$}{heat transfer coefficient\nomunit{$\mathrm{W/(m^2K)}$}}
%\nomenclature[Ah2]{$h$}{specific enthalpy\nomunit{$\mathrm{J/kg}$}}
\nomenclature[Aj]{$\mathbf{j}$}{flux vector\nomunit{$\mathrm{m/s}$}}
\nomenclature[AL]{$L$}{characteristic length\nomunit{$\mathrm{m}$}}
\nomenclature[Al]{$l$}{length\nomunit{$\mathrm{m}$}}
\nomenclature[AM]{$M$}{torque\nomunit{$\mathrm{Nm}$}}
\nomenclature[Am]{$m$}{mass\nomunit{$\mathrm{kg}$}}
\nomenclature[AN]{$N$}{number of particles}
\nomenclature[An2]{$\mathbf{n}$}{unit normal vector}
\nomenclature[Ap]{$p$}{pressure\nomunit{$\mathrm{Pa}$}}
\nomenclature[Aq]{$q$}{heat flux\nomunit{$\mathrm{W/m^2}$}}
\nomenclature[Aqm]{$q_m$}{mass flow rate\nomunit{$\mathrm{kg/s}$}}
\nomenclature[Ar]{$r$}{radius\nomunit{$\mathrm{m}$}}
\nomenclature[AT]{$T$}{temperature\nomunit{$\mathrm{K}$}}
\nomenclature[At]{$t$}{time\nomunit{$\mathrm{s}$}}
\nomenclature[AV]{$V$}{volume\nomunit{$\mathrm{m^3}$}}
\nomenclature[Av]{$v$}{velocity magnitude\nomunit{$\mathrm{m/s}$}}
\nomenclature[Av2]{$\mathbf{v}$}{velocity vector\nomunit{$\mathrm{m/s}$}}
\nomenclature[Ax]{$x$}{x-coordinate (width)\nomunit{$\mathrm{m}$}}
\nomenclature[Ay]{$y$}{y-coordinate (depth)\nomunit{$\mathrm{m}$}}
\nomenclature[Az]{$z$}{z-coordinate (height)\nomunit{$\mathrm{m}$}}
% B=Greek symbols
%\nomenclature[Ba]{$\alpha$}{thermal expansion coefficient\nomunit{$\mathrm{1/K}$}}
\nomenclature[Ba]{$\alpha$}{(alfa)\nomunit{$\mathrm{1/K}$}}
\nomenclature[Bb]{$\beta$}{(beta)}
\nomenclature[BG]{$\Gamma$}{(Gamma)}
\nomenclature[Bg]{$\gamma$}{(gamma)}
\nomenclature[BD1]{$\Delta$}{(Delta) usually used for change/difference}
\nomenclature[BD2]{$\varDelta$}{(varDelta)}
\nomenclature[Bd3]{$\delta$}{(delta) notice the difference to $\partial$ (partial differential)}
\nomenclature[Be1]{$\epsilon$}{(epsilon)}
\nomenclature[Be2]{$\upepsilon$}{(upepsilon)}
\nomenclature[Bz]{$\zeta$}{(zeta)}
\nomenclature[Be3]{$\eta$}{(eta)}
\nomenclature[Bth]{$\theta$}{(theta)}
\nomenclature[BTh]{$\Theta$}{(Theta)}
\nomenclature[Bth2]{$\vartheta$}{(vartheta)}
\nomenclature[Bi]{$\iota$}{(iota)}
\nomenclature[Bk]{$\kappa$}{(kappa)}
\nomenclature[BL]{$\Lambda$}{(Lambda)}
\nomenclature[Bl]{$\lambda$}{(lambda)}
\nomenclature[Bm]{$\mu$}{(mu)}
\nomenclature[Bm2]{$\upmu$}{(upmu)}
\nomenclature[Bn]{$\nu$}{(nu)}
\nomenclature[BX]{$\Xi$}{(Xi)}
\nomenclature[Bx]{$\xi$}{(xi)}
\nomenclature[BP]{$\Pi$}{(Pi)}
\nomenclature[Bp]{$\pi$}{(pi) e.g. pressure ratio, note the difference with (uppi) constant $\uppi=3.14\ldots$}
\nomenclature[Br]{$\rho$}{(rho)}
\nomenclature[Br2]{$\uprho$}{(uprho)}
\nomenclature[BS]{$\Sigma$}{(Sigma)}
\nomenclature[Bs]{$\sigma$}{(sigma)}
\nomenclature[Bs2]{$\varsigma$}{(varsigma)}
\nomenclature[Bta]{$\tau$}{(tau)}
\nomenclature[Bu]{$\upsilon$}{(upsilon)}
\nomenclature[Bph]{$\phi$}{(phi)}
\nomenclature[BPh]{$\Phi$}{(Phi)}
\nomenclature[Bph2]{$\varphi$}{(varphi)}
\nomenclature[BX]{$\chi$}{(chi)}
\nomenclature[BPs]{$\Psi$}{(Psi)}
\nomenclature[Bps]{$\psi$}{(psi)}
\nomenclature[BO]{$\Omega$}{(Omega)}
\nomenclature[Bo]{$\omega$}{(omega)}
% C=Subscripts
\nomenclature[Ce]{eff}{effective}
\nomenclature[Cma]{max}{maximum}
\nomenclature[Cmi]{min}{minimum}
\nomenclature[Cg]{g}{gas}
\nomenclature[Ct]{tot}{total}
\nomenclature[Cp]{p}{particle}
\nomenclature[Cs]{s}{solid}
\nomenclature[Cl]{l}{liquid}
% D=Superscripts
\nomenclature[Dp]{p}{partial layer}
\nomenclature[Ds]{*}{dimensionless}
% E=Abbreviations
\nomenclature[E2]{2D}{two dimensional}
\nomenclature[E3]{3D}{three dimensional}
\nomenclature[Ec]{CFD}{computational fluid dynamics}
\nomenclature[El]{LES}{large eddy simulation}
\nomenclature[Ep]{PDF}{probability density function}
% F=Dimensionless
\nomenclature[FAr]{Ar}{Archimedes number}
\nomenclature[FBi]{Bi}{Biot number}
\nomenclature[FFO]{Fo}{Fourier number}
\nomenclature[FGr]{Gr}{Grashof number}
\nomenclature[FNu]{Nu}{Nusselt number}
\nomenclature[FPr]{Pr}{Prandtl number}
\nomenclature[FRe]{Re}{Reynolds number}
\nomenclature[FSh]{Sh}{Sherwood number}
\nomenclature[FSt1]{St}{Stanton number}
\nomenclature[FSte]{Ste}{Stefan number}
\nomenclature[FStk]{Stk}{Stokes number}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Start of Introduction section %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


In today's rapidly evolving landscape of software development, open-source software has become a transformative force \cite{fitzgerald2006transformation}. Its collaborative model fuels innovation by making code accessible, fostering a global community of developers, and lowering barriers to entry. 

The widespread adoption of the internet created a natural environment for open-source collaboration and distribution \cite{schweik2012internet}. Additionally, the emergence of cloud computing and agile methodologies has further streamlined the development process, empowering developers to build and deploy open-source solutions with unprecedented speed and flexibility \cite{raj2013envisioning}.

Moreover, the exponential growth of data highlights the need for solutions capable of handling vast amounts of information \cite{berman2013principles}. This need drives the development of fields such as big data and data science, which often rely heavily on open-source tools and libraries.

The accessibility and adaptability of open source software have democratized the software landscape. It offers a valuable alternative to proprietary solutions, particularly for individuals, start-ups, and organizations with limited resources. The collaborative nature of open-source development often leads to rapid innovation and the creation of robust, secure, and continuously improving software solutions.

While the benefits of open-source software are widely recognized - from its cost-effectiveness and adaptability to enhanced security and strong community support – the motivations that drive developers to contribute their time and expertise to these projects remain less understood.  This gap in our understanding highlights an important question: why do companies and individuals dedicate themselves to creating and maintaining the open-source software that powers so much of our digital world?

Investigating this question is crucial for several reasons. Understanding developer motivations offers insights into how we can ensure the long-term sustainability of open-source projects. Furthermore, companies and organizations hoping to attract top talent within the open-source space would benefit from knowing what drives developer participation within these communities.  Uncovering these motivations can also shed light on how open-source projects function, how collaboration occurs, and how knowledge is shared and developed.

\subsection{Objectives}

This research project ventures beyond the surface of open-source software development, delving into the intricate web of motivations that drives developers within this collaborative community. By employing a multifaceted approach that combines empirical analysis with in-depth qualitative inquiries, the study seeks to illuminate the underlying forces that propel developers to contribute. These forces encompass not only the tangible incentives but also the value systems and socio-technical factors that influence their engagement. Ultimately, this investigation aims to provide a more nuanced understanding of the dynamics that shape the ever-evolving landscape of modern software development, with a specific focus on the crucial role played by open-source communities.

\subsection{Motivation}

As a former software engineer engrossed in the dynamic world of software development, my daily experience was enriched by the constant use of open-source software. From leveraging fundamental frameworks like ReactJS from Facebook to seamlessly integrating libraries and packages sourced from NPM, open-source solutions became an indispensable aspect of my workflow. Their ubiquitous presence became so ingrained in my routine that their influence often went unnoticed, seamlessly woven into the fabric of my daily tasks. However, as I transition into the realm of program software product management, I find myself drawn to exploring a new frontier – one that encompasses not only the technical aspects but also delves into the world of human psychology. It is this intersection of technology and human behavior that piques my curiosity and drives my desire to embark on this research endeavor. 

Through this thesis, I aspire to investigate the nuanced interplay between open-source software adoption and the human factors influencing developer behavior and decision-making processes. By unraveling these complexities, I aim to contribute to a deeper understanding of how human elements shape the adoption, utilization, and evolution of open-source software, ultimately informing more effective software product management strategies.


\clearpage  % This command will start the next section from the new page
