%% Appendix 7
\pagenumbering{arabic}  % This will reset the page numbering
\thispagestyle{empty} % use this if pagenumber needs to be removed
\section{Publishing the thesis}\label{App:G}

LUT’s degree regulations state that Bachelor's and Master's theses are public documents. They are published in the LUTPub repository, and related instructions are available on the \href{https://libguides.lut.fi/lutpub-en}{\textcolor{blue}{library website}}.

Together with the first examiner, make sure that the commissioner of your thesis is aware of the publicity requirements from the very beginning of the discussions. The student writing the thesis and the thesis commissioner are responsible for ensuring that there is no confidential material in the thesis. The background material of the thesis may contain confidential content. The background material is not public.

All theses in LUTPub must fulfill accessibility requirements. Your text must be as legible as possible to readers. Remember:
\begin{itemize}
    \item to use \LaTeX~commands for headings,
    \item embed hyperlinks into your text or a description of the linked content; do not include URL addresses,
    \item add/check the alt text of your figures and tables describing briefly the main content in writing.
    \item to refer to each figure and table in the text, and verbally describe in the text the key content presented in the figures and tables.
\end{itemize}

At the moment (09/2023), \LaTeX~text system and its add-ons (packages) can only produce pdf files according to accessibility criteria to a limited extent. Using the \LaTeX~ system, it is not possible to produce a final product that meets all accessibility criteria and works universally. Due to deficiencies, the automatic read-out of the PDF file may have problems, especially with images, tables, and equations. For this reason, it is especially important that the contents of floating objects (images, tables, and equations) are described as clearly as possible in the body text.

\clearpage % This command will start the next section from the new page